---
title: "Workflow"
author: "Jalil Rasgado; Apurva Shah"
date: "2020-10-22"
output: workflowr::wflow_html
editor_options:
  chunk_output_type: console
---

To reproduce the results, please follow the following, using codes we provided.

## Method to processing

The preprocessing of DWI and T1 images included initial manual quality assessment and conversion from dicom to nifti format.

## T1-weighted preprocessing

The T1w images were then processed and parcellated into 86 regions of interest (ROIs) (68 cortical and 18 sub-cortical) of the Desikan atlas using Freesurfer 6.0. The pre-processing steps involved skull striping, bias correction, and tissue segmentation. Subsequently, surface-based non-linear registration to map the cortical sulci-gyri and volume-based registration for subcortical structures were performed.
 
```{bash, eval=FALSE, engine="sh"}
#! /bin/bash

DIR=$PWD	#Base directory path
List=${DIR}/Subjects.txt	#List of Subjects

for Sub in `cat ${List}`
do
echo ${Sub}

T1_Nifti=${DIR}/NIFTIs/${Sub}/sub-${Sub}_T1w.nii.gz	#Raw T1 structural data

mkdir -p ${DIR}/Freesurfer/${Sub}		
export SUBJECTS_DIR=${DIR}/Freesurfer
mkdir -p ${SUBJECTS_DIR}/${Sub}/mri/orig

rm ${SUBJECTS_DIR}/${Sub}/scripts/IsRunning.lh+rh

mri_convert ${T1_Nifti} ${SUBJECTS_DIR}/${Sub}/mri/orig/001.mgz		#converting nifti to mgz

cd ${SUBJECTS_DIR}
recon-all -all -s ${Sub}		#perform T1 preprocessing and Compute Parcellation of whole brain

mri_convert ${SUBJECTS_DIR}/mri/brain.mgz ${SUBJECTS_DIR}/mri/nifti/brain.nii.gz
mri_convert ${SUBJECTS_DIR}/mri/aparc+aseg.mgz ${SUBJECTS_DIR}/freeLabels.nii.gz

done
```


## Diffusion weighted preprocessing

DWI volumes were preprocessed using FSL 6.0.11 (https://fsl.fmrib.ox.ac.uk). Initial steps included correction of eddy current artifacts and motion noise induced by eddy currents using “eddy_correct” which employed affine transformation to diffusion gradient images to the baseline b=0 image and distortion correction using “topup”. Based on the rotation parameters in the transformation, the gradients were rotated to match the transformed images. Subsequently, the brain extraction was performed using the brain extraction too. To map WM regions we employed the JHU-WM atlas which contains 20 tracts defined in MNI space.

```{bash, eval=FALSE, engine="sh"}
#! /bin/bash

FSLOUTPUTTYPE=NIFTI_GZ
export FSLOUTPUTTYPE

DIR=$PWD   #Base directory path
DTI_dir=${DIR}/NIFTIs		#Raw data Directory
index=${DIR}/Index.txt		#acqp indexor each DWI volume
acqp=${DIR}/aqcp_Param.txt	#DWI aqcusition parametes

List=${DIR}/Subjects.txt

for Sub in `cat ${List}`
do
echo ${Sub}

mkdir -p ${DIR}/BedpostX/${Sub}
Sub_dir=${DIR}/BedpostX/${Sub}

cp -rf ${DTI_dir}/${Sub}/sub-${Sub}_dwi.nii.gz ${Sub_dir}/${Sub}_DWI.nii.gz
DWI=${Sub_dir}/${Sub}_DWI.nii.gz
bvc=${DTI_dir}/${Sub}/sub-${Sub}_dwi.bvec
bvl=${DTI_dir}/${Sub}/sub-${Sub}_dwi.bval

echo "Distortion Correction......"

mkdir -p ${Sub_dir}/${Sub}/dwi_volumes
mkdir -p ${Sub_dir}/${Sub}/epi-1_volumes

fslsplit ${Sub_dir}/${Sub}/sub-${Sub}_dwi.nii.gz ${Sub_dir}/${Sub}/dwi_volumes/sub-${Sub}_dwi_x -t 
fslsplit ${Sub_dir}/${Sub}/sub-${Sub}_run-01_epi.nii.gz ${Sub_dir}/${Sub}/epi-1_volumes/sub-${Sub}_run-01_epi_x -t 

cp -rf ${Sub_dir}/${Sub}/dwi_volumes/sub-${Sub}_dwi_x0000.nii.gz ${Sub_dir}/${Sub}/dwi_volumes/sub-${Sub}_no_diff_PA.nii.gz
cp -rf ${Sub_dir}/${Sub}/epi-1_volumes/sub-${Sub}_run-01_epi_x0000.nii.gz ${Sub_dir}/${Sub}/epi-1_volumes/sub-${Sub}_no_diff_AP.nii.gz

fslmerge -t ${Sub_dir}/${Sub}/${Sub}_PA-AP_no_diff.nii.gz ${Sub_dir}/${Sub}/dwi_volumes/sub-${Sub}_no_diff_PA.nii.gz ${Sub_dir}/${Sub}/epi-1_volumes/sub-${Sub}_no_diff_AP.nii.gz

topup --imain=${Sub_dir}/${Sub}/${Sub}_PA-AP_no_diff.nii.gz --datain=${Sub_dir}/${Sub}/aqcp_PAAP.txt --out=${Sub_dir}/${Sub}/${Sub}_PA-AP_no_diff_corrected_1 --iout=${Sub_dir}/${Sub}/${Sub}_PA-AP_no_diff_corrected
fslmaths ${Sub_dir}/${Sub}/${Sub}_PA-AP_no_diff_corrected -Tmean ${Sub_dir}/${Sub}/${Sub}_PA-AP_no_diff_corrected
bet ${Sub_dir}/${Sub}/${Sub}_PA-AP_no_diff_corrected ${Sub_dir}/${Sub}/${Sub}_PA-AP_no_diff_corrected_brain -f 0.45 -m -R

echo "Eddy-corraction and bvec rotation..."
eddy_openmp --imain=${Sub_dir}/${Sub}_SS --mask=${Sub_dir}/${Sub}/${Sub}_PA-AP_no_diff_corrected_brain_mask --acqp=${acqp} --index=${index} --topup=${Sub_dir}/${Sub}/${Sub}_PA-AP_no_diff_corrected_1 --bvecs=${bvc} --bvals=${bvl} --out=${Sub_dir}/${Sub}_eddy

echo "Brain Mask Creation..."
bet ${Sub_dir}/${Sub}_eddy ${Sub_dir}/brain_output -f 0.15 -m -F -R
fslmaths ${Sub_dir}/${Sub}_eddy -mul ${Sub_dir}/brain_output_mask ${Sub_dir}/${Sub}_eddy_SS

echo "Tensor Modeling..."
dtifit -k ${Sub_dir}/${Sub}_eddy_ss.nii.gz -o ${Sub_dir}/${Sub}_DWI -m ${Sub_dir}/brain_output_mask -r ${Sub_dir}/${Sub}_eddy.eddy_rotated_bvecs -b ${bvl}

cp -rf ${bvl} ${Sub_dir}/${Sub}/sub-${Sub}_dwi_eddy_SS.bval 
cp -rf ${Sub_dir}/${Sub}_eddy.eddy_rotated_bvecs ${Sub_dir}/${Sub}/sub-${Sub}_dwi_eddy_SS.bvec 
```

## Extracting Viso values 

 used the neurite orientation dispersion and density imaging (NODDI) method that employs a three-compartment model to understand brain tissue microstructure in detail. NODDI produces three metrics that quantify: (1) the fractional volume of extracellular fluid (isotropic volume fraction [Viso]), (2) intracellular neurite dispersion (orientation dispersion index [ODI]) and (3) neurite density (volume fraction [Vic]), after eliminating effects of extracellular fluid [ref]. We employed the NODDI toolbox in MATLAB (http://mig.cs.ucl.ac.uk/index.php?n=Tutorial.NODDImatlab) on preprocessed DWI images. 

```{bash, eval=FALSE, engine="sh"}
clc;
clear all;

%%
DIR = pwd;

Sub_list = [DIR '/OpenNeuro_FWE/Subjects.txt'
fid=fopen(Sub_list,'r');
ID=fscanf(fid,'%f',[1 131]);
fclose(fid);
for i=1:length(ID)
    fprintf('loading the data.....\n');
    DWI = [DIR '/OpenNeuro_FWE/' num2str(ID(i)) '/' num2str(ID(i)) '_DWI_eddy_SS.nii.gz'];
    Mask = [DIR '/OpenNeuro_FWE/' num2str(ID(i)) '/' num2str(ID(i)) '_DWI_brain_mask.nii.gz'];
    gunzip(DWI,[DIR '/OpenNeuro_FWE/' num2str(ID(i))]);
    gunzip(Mask,[DIR '/OpenNeuro_FWE/' num2str(ID(i))]);
    DWI = [DIR '/OpenNeuro_FWE/' num2str(ID(i)) '/' num2str(ID(i)) '_DWI_eddy_SS.nii'];
    Mask = [DIR '/OpenNeuro_FWE/' num2str(ID(i)) '/' num2str(ID(i)) '_DWI_brain_mask.nii'];
    bvecs = [DIR '/OpenNeuro_FWE/' num2str(ID(i)) '/' num2str(ID(i)) '_DWI_eddy_SS.bval'];
    bvals = [DIR '/OpenNeuro_FWE/' num2str(ID(i)) '/' num2str(ID(i)) '_DWI_eddy_SS.bvec'];
    ROI = [DIR '/OpenNeuro_FWE/' num2str(ID(i)) '/' num2str(ID(i)) '_DWI_NODDI_roi.mat'];
    Fitted_Param = [DIR '/OpenNeuro_FWE/' num2str(ID(i)) '/' num2str(ID(i)) '_DWI_FittedParams.mat'];
    Out = [DIR '/OpenNeuro_FWE/' num2str(ID(i)) '/' num2str(ID(i)) '_DWI_NoddiFit'];
    fprintf('creating the ROI.....\n');
    CreateROI(DWI, Mask, ROI);
    fprintf('defining the protocol.....\n');
    DWI_protocol = FSL2Protocol(bvecs, bvals);
    fprintf('defining the model.....\n');
    noddi_model = MakeModel('WatsonSHStickTortIsoV_B0');   
    fprintf('fitting the NODDI model to the data.....\n');
    batch_fitting(ROI, DWI_protocol, noddi_model, Fitted_Param, 4);
    fprintf('writing the fitted parameters to nii files.....\n');
    SaveParamsAsNIfTI(Fitted_Param, ROI, Mask, Out);
end
```

## Diffusion FWE analysis

These 86 ROIs were translated to the diffusion space by employing a symmetric diffeomorphic transformation model (SyN) using Advanced Normalization Tools (ANTs). We extract at the end the ROIs values from data processings

```{bash, eval=FALSE, engine="sh"}
#! /bin/bash


DIR=$PWD

mkdir ${DIR}/freeROI_FW_1
mkdir ${DIR}/jhuTract_FW_1
mkdir ${DIR}/jhuWM_FW_1
mkdir ${DIR}/JHUroi_FW_1

List=${DIR}/Subjects.txt	#List of Subjects

for Sub in `cat ${List}`
do
echo ${i}

fslstats -t ${DIR}/${i}/${i}_DWI_NoddiFit_fiso -M >> ${DIR}/OpenNeuro_FW_mean.txt		#Compute mean FW for Wholebrain
fslstats -t ${DIR}/${i}/${i}_DWI_NoddiFit_ficvf -M >> ${DIR}/OpenNeuro_ficv_mean.txt	#Compute mean icvf for Wholebrain
fslstats -t ${DIR}/${i}/${i}_DWI_NoddiFit_odi -M >> ${DIR}/OpenNeuro_odi_mean.txt		#Compute mean odi for Wholebrain


echo "extract FW for Structural Rois" 

antsRegistrationSyN.sh -f ${DIR}/${i}/FWE_DTI/${i}_DWI_FA.nii.gz -m ${DIR}/Freesurfer/${Sub}/mri/nifti/brain.nii.gz -t s -o ${DIR}/${i}/FWE_DTI/${i}_DWI2T1 -n 8	#Compute Registration between DWI and Structural bain
antsApplyTransforms -i ${DIR}/Freesurfer/${Sub}/freeLabels.nii.gz -r ${DIR}/${i}/FWE_DTI/${i}_DWI_FA.nii.gz -o ${DIR}/${i}/FWE_DTI/${i}_T12DWI.nii.gz -t [${DIR}/${i}/FWE_DTI/${i}_DWI2T10GenericAffine.mat, 0] -t  ${DIR}/${i}/FWE_DTI/${i}_DWI2T11Warp.nii.gz -n NearestNeighbor	


list=/home/scmia/Documents/OpenNeuro/86_labels.txt	# list of Desikan Structural brain rois (68 cortical + 18 sub cortical)
mkdir ${DIR}/${i}/labelMASKS_DWI
for j in `cat ${list}`;do
echo $j
fslmaths ${DIR}/${i}/FWE_DTI/${i}_T12DWI.nii.gz -uthr ${j} -thr ${j} ${DIR}/${i}/labelMASKS_DWI/${j}_mask_dwi.nii.gz
fslstats -t ${DIR}/${i}/${i}_DWI_NoddiFit_fiso -k ${DIR}/${i}/labelMASKS_DWI/${j}_mask_dwi.nii.gz -M >> ${DIR}/freeROI_FW_1/${j}_FW.txt		#Compute mean FW for structure rois
done
fslstats -t ${DIR}/${i}/${i}_DWI_NoddiFit_fiso -k ${DIR}/${i}/labelMASKS_DWI/CC_mask_dwi.nii.gz -M >> ${DIR}/freeROI_FW_1/CC_FW.txt

echo "extract FW for JHU Rois" 

antsRegistrationSyN.sh -f ${DIR}/${i}/FWE_DTI/${i}_DWI_FA.nii.gz -m ${FSLDIR}/data/atlases/JHU/JHU-ICBM-FA-1mm.nii.gz -t s -o ${DIR}/${i}/FWE_DTI/${i}_DWI2JHU -n 8		# comupute registration between 

antsApplyTransforms -i ${FSLDIR}/data/atlases/JHU/JHU-ICBM-tracts-maxprob-thr25-1mm.nii.gz -r ${DIR}/${i}/FWE_DTI/${i}_DWI_FA.nii.gz -o ${DIR}/${i}/FWE_DTI/${i}_JHU2DWI.nii.gz -t [${DIR}/${i}/FWE_DTI/${i}_DWI2JHU0GenericAffine.mat, 0] -t  ${DIR}/${i}/FWE_DTI/${i}_DWI2JHU1Warp.nii.gz -n NearestNeighbor		#apply registration to JHU tract atlas

antsApplyTransforms -i ${FSLDIR}/data/atlases/JHU/JHU-ICBM-labels-1mm.nii.gz -r ${DIR}/${i}/FWE_DTI/${i}_DWI_FA.nii.gz -o ${DIR}/${i}/FWE_DTI/${i}_JHUlabels2DWI.nii.gz -t [${DIR}/${i}/FWE_DTI/${i}_DWI2JHU0GenericAffine.mat, 0] -t  ${DIR}/${i}/FWE_DTI/${i}_DWI2JHU1Warp.nii.gz -n NearestNeighbor		#apply registration to JHU wm atlas

mkdir ${DIR}/${i}/FWE_DTI/JHU_dwi
for k in {1..20} ; do
echo ${k}
fslmaths ${DIR}/${i}/FWE_DTI/${i}_JHU2DWI.nii.gz -uthr ${k} -thr ${k} ${DIR}/${i}/FWE_DTI/JHU_dwi/${k}_jhu2dwi_tract.nii.gz		#Extract JHU tract rois individual 
fslstats -t ${DIR}/${i}/${i}_DWI_NoddiFit_fiso -k ${DIR}/${i}/FWE_DTI/JHU_dwi/${k}_jhu2dwi_tract.nii.gz -M >> ${DIR}/jhuTract_FW_1/${k}_tract_FW.txt	#Compute mean FW for JHU tract rois
done

mkdir ${DIR}/${i}/FWE_DTI/JHU_WM_dwi
for k in {1..48} ; do
echo ${k}
fslmaths ${DIR}/${i}/FWE_DTI/${i}_JHUlabels2DWI.nii.gz -uthr ${k} -thr ${k} ${DIR}/${i}/FWE_DTI/JHU_WM_dwi/${k}_jhuWM2dwi_tract.nii.gz	#Extract JHU wm rois individual 
fslstats -t ${DIR}/${i}/${i}_DWI_NoddiFit_fiso -k ${DIR}/${i}/FWE_DTI/JHU_WM_dwi/${k}_jhuWM2dwi_tract.nii.gz -M >> ${DIR}/jhuWM_FW_1/${k}_WMroi_FW.txt		#Compute mean FW for JHU wm rois
done

done
```

## Plot the results

To plot the Viso-values differences between structures in two groups we use the next libraries:

```{r echo=TRUE, message=FALSE, warning=FALSE}
library(ggseg)
library(ggsegJHU)
dk$region[-c(2,8,9,31,34,10,12,15,73,74,53,75,80,60,81,61,83,87)]<-NA
ggseg(atlas = dk, mapping = aes(fill=region),
      position = "stacked", colour = "black", 
      show.legend = F,size=0.7) + scale_fill_brain("dk")

aseg$region[-c(15,28)]<-NA
ggseg(atlas=aseg,mapping=aes(fill=region),show.legend = F,
      colour="black",size=0.7) + scale_fill_brain("aseg")

jhu$region[-c(9,12,14,22,23,35,40)]<-NA
ggseg(atlas = jhu, mapping = aes(fill = region),colour="black",size=0.7,show.legend=F) +
  scale_fill_brain("jhu", package = "ggsegJHU")

```

### Tables

```{r echo=TRUE, message=FALSE, warning=FALSE}
library(kableExtra)
library(formattable)
datos.struc<-read.csv(paste0(getwd(),"/data/OpenN_FW_noddi_analysis_results_3.csv"))
colnames(datos.struc)<-c("Region","Group","mean","sd","p-value")
datos.struc.GM<-datos.struc[-c(1:14),]
rownames(datos.struc.GM)<-NULL
datos.struc.GM$Region<-c("Superior temporal sulcus L","Superior temporal sulcus L","lateral orbitofrontal L","lateral orbitofrontal L",
                         "middle temporal L","middle temporal L","parahippocampal L","parahippocampal L",
                         "pars opercularis L","pars opercularis L","pars triangularis L","pars triangularis L",
                         "rostral middle frontal L","rostral middle frontal L","pallidum L","pallidum L",
                         "inferior parietal R","inferior parietal R","inferior temporal R","inferior temporal R",
                         "lateral occipital R","lateral occipital R","pars triangularis R","pars triangularis R",
                         "postcentral R","postcentral R","posterior cingulate R","posterior cingulate R",
                         "rostral middle frontal R","rostral middle frontal R","supramarginal R","supramarginal R",
                         "cerebellum cortex R","cerebellum cortex R")

datos.struc.GM$mean<-color_bar(alpha(c("#196428","#196428","#234b32","#234b32",                                "#a06432","#a06432","#14dc3c","#14dc3c","#dcb48c","#dcb48c",
                                      "#dc3c14","#dc3c14",
                                      "#4b327d","#4b327d","#0c30ff","#0c30ff",                                      "#dc3cdc","#dc3cdc","#b42878","#b42878","#141e8c","#141e8c",
                                      "#dc3c14","#dc3c14",
                                      "#dc1414","#dc1414","#dcb4dc","#dcb4dc",                                    "#4b327d","#4b327d","#50a014","#50a014","#dcf8a4","#dcf8a4"),0.75))(datos.struc.GM$mean)
tabla.GM<-kable(datos.struc.GM, escape = F) %>% kable_minimal(full_width = F) %>%
  column_spec(1, bold = T, width = "5.5cm") %>%
  column_spec(2,color = c("#5fadc2","#3d6470")) %>%
  column_spec(3, color="black",width = "4cm") %>%
  collapse_rows(columns = c(1,5))
tabla.GM
```

```{r echo=TRUE, message=FALSE, warning=FALSE}
datos.struc.WM<-datos.struc[c(1:14),]
rownames(datos.struc.WM)<-NULL
datos.struc.WM$Region<-c("cingulum gyrus L","cingulum gyrus L","cingulum gyrus hippocampus R","cingulum gyrus hippocampus R",
                         "forceps minor","forceps minor",
                         "superior longitudinal fasciculus L", "superior longitudinal fasciculus L","medial lemniscus R","medial lemniscus R",
                         "medial lemniscus L","medial lemniscus L","uncinate fasciculus L","uncinate fasciculus L")
datos.struc.WM$mean<-color_bar(alpha(c("#00ff40","#00ff40","#ffcc00","#ffcc00","#c4ff00","#c4ff00",
                                       "#eaff00","#eaff00","#9568e0","#9568e0","#9568e0","#9568e0","#0040ff","#0040ff"),0.75))(datos.struc.WM$mean)
tabla.WM<-kable(datos.struc.WM, escape = F) %>% kable_minimal(full_width = F) %>%
  column_spec(1, bold = T, width = "5.5cm") %>%
  column_spec(2,color = c("#5fadc2","#3d6470")) %>%
  column_spec(3, color="black",width = "4cm") %>%
  collapse_rows(columns = c(1,5))
tabla.WM
```


## Global correlation with clinical measures

After extract NODDI values, in this case Viso-NODDI. We merged them in a csv table in order to calculate the analysis of interest. We also load the clinical metrics

```{r echo=TRUE, message=FALSE, warning=FALSE}
# loading the libraries needed
library(tidyverse)
library(tibble)
library(Hmisc)
library(corrplot)

noddi<-read.csv(paste0(getwd(),"/data/OpenN_FW_noddi_analysis_3.csv"))
clinicals<-read.csv(paste0(getwd(),"/data/Conn_database_clinicals_fwi.csv"))
```

Filter for only Cocaine use disorder group and make the analysis.

```{r}
data.noddi<-noddi %>% filter(Group==2) %>% select(-c("Id","Group","Age","Sex"))
data.clinicals<-clinicals %>% filter(grupo==2) %>% select(-c("RID","grupo",
                                                             "age","sex","educ"))
data.noddi[is.na(data.noddi)]<-0
data.clinicals[is.na(data.clinicals)]<-0
data.clinic<-data.clinicals[-c(5:6,15:19,44:52,55)]
data.together<-data.frame(data.clinic,data.noddi)
rcor.viso.clinic<-rcorr(as.matrix(data.together), type = c("pearson"))
p.adj.viso.clinic<-p.adjust(rcor.viso.clinic$P, method = "fdr", 
                            n = length(rcor.viso.clinic$P))
resAdj.viso.clinic <- matrix(p.adj.viso.clinic, ncol = dim(rcor.viso.clinic$P)[1])
r.cor.ros.len<-rcor.viso.clinic$r[,]

## You can save them in csv or plot them using corrplot
#write.csv(rcor.viso.clinic$r,"rcor.csv", row.names = TRUE)
#write.csv(rcor.viso.clinic$P,"pcor.csv")
#write.csv(resAdj.viso.clinic,"padcor2.csv", row.names = TRUE)
```

## Partial correlation using covariables

To calculate partial correlation, we use Education and Sex as covariables. Taking cocaine use pattern, tobacco total years, CCQ, BIS, ASIP

```{r message=FALSE, warning=FALSE}
data.noddi<-noddi %>% filter(Group==2) 
data.clinicals<-clinicals %>% filter(grupo==2) 
data.noddi<-data.noddi[-c(1:4)]
data.clinicals<-data.clinicals[-c(1:2)]
data.clinicals[is.na(data.clinicals)]<-0
data.clinic<-data.clinicals[-c(1:4,8:9,11,18:55,58)]
clin<-1:ncol(data.clinic)
nods<-1:ncol(data.noddi)
structures<-colnames(data.noddi)
score.clini<-colnames(data.clinic)

library(ppcor)
pctest.noddi.clinical<-lapply(clin,function(y) sapply(nods, function(x) pcor.test(data.noddi[x],data.clinic[y],list(data.clinicals$educ,data.clinicals$sex), method="pearson")))

pc.nclin<-lapply(pctest.noddi.clinical, head, 1)
pc.nclins<-lapply(pc.nclin,setNames,structures)
r.pcor<-bind_rows(pc.nclins)
rownames(r.pcor)<-score.clini

ppc.nclin<-lapply(pctest.noddi.clinical, `[`, 2, )
ppc.nclinr<-lapply(ppc.nclin,function(d) rbind(d))
ppc.nclins<-lapply(ppc.nclinr,setNames,structures)
p.pcors<-bind_rows(ppc.nclins)
rownames(p.pcors)<-score.clini

p.pcors<-data.matrix(p.pcors)
ppvalues.bc<-p.pcors[which(p.pcors<=0.05)]
matrixr.pcor<-data.matrix(r.pcor)
#write.csv(p.pcors,"p_pcors.csv", row.names = TRUE)
#write.csv(matrixr.pcor,"matrixr_pcor.csv", row.names = TRUE)

```

After calculated it, we can load it in a superheat plot, only checking the p-values > 0.05, and add it in a csv table, for non significant we put 0-values

```{r}
library(superheat)
clin.cor.r2<-read.csv(paste0(getwd(),"/data/dataclin8_final.csv"))
m.clin.cor.r<-data.matrix(clin.cor.r2[,-c(1,2,3)])
gears <- paste(clin.cor.r2$Area, "Matter")
rownames(m.clin.cor.r)<-clin.cor.r2$Region
colnames(m.clin.cor.r)<-c("Age onset","week dose",
                          "Cognitive","Motor","Non planned","Total score")

superheat(m.clin.cor.r, 
                  pretty.order.rows = TRUE,
                  pretty.order.cols = FALSE,
                  heat.pal = c("#005e91", "white","#c43333"),
                  heat.na.col = "white",
                  n.clusters.rows = 2,
                  membership.rows = gears, #puesto a mano, borrar si se desea hacer por kmeans
                  left.label = "variable",
                  left.label.col = "white",
                  row.title.size = 6,
                  bottom.label.text.angle = 90,
                  column.title.size = 6,
                  yr = clin.cor.r2$FW,
                  yr.axis.name = "Viso Values",
                  yr.axis.size = 15,
                  yr.plot.type = "bar",
                  yr.bar.col = "black",
                  X.text = as.matrix(m.clin.cor.r),
                  yr.cluster.col = c("#65767b","#93c6d4"),
                  bottom.label.col = c("#b3e2cd","#b3e2cd",
                                       "#b6a3c8","#b6a3c8","#b6a3c8","#b6a3c8"),
                  bottom.label.size = 0.20042)
```


## Data exploration

### Cocaine onset and dosage

In order to check distribution of data based of previous results we plot the associated regions of both measures

```{r}
library(psych)
data.noddi<-noddi[-c(1,3,4)] %>% filter(Group==2)
orb.ifgtri<-data.noddi[c("lh_lateralorbitofrontal","lh_parstriangularis")]
coc.onset.dose<-data.clinicals[c(3,4)]
both.coc<-data.frame(coc.onset.dose[1],orb.ifgtri)

pairs.panels(both.coc, 
             method = "pearson", # correlation method
             hist.col = "#00AFBB",
             lm = TRUE,
             density = TRUE,  # show density plots
             ellipses = TRUE # show correlation ellipses
)

sfl.unci.pcg<-data.noddi[c("SFL_L","Unci_L","rh_posteriorcingulate")]
both.coc<-data.frame(coc.onset.dose[2],sfl.unci.pcg)

pairs.panels(both.coc, 
             method = "pearson", # correlation method
             hist.col = "#00AFBB",
             lm = TRUE,
             density = TRUE,  # show density plots
             ellipses = TRUE # show correlation ellipses
)
```


## Multiple regression

```{r}
library(MASS)
data.clinicals<-clinicals %>% filter(grupo==2) 
data.clinic<-data.clinicals[c("sex","age","educ","coc.age.onset","week.dose","years.begin",
              "tobc.totyears","ccqn.score","ccqg.score","BIS_cog","BIS_mot","BIS_nonp",
              "BIS_tot_score","ASIP_alcohol_use","ASIP_drugs_use","ASIP_psychiatric")]
data.clinic[is.na(data.clinic)]<-0
frame.noddi<-data.frame(data.noddi[c("Unci_L","SFL_L","lh_parsopercularis","lh_bankssts",
                                     "lh_rostralmiddlefrontal","rh_rostralmiddlefrontal",
                                     "rh_lateraloccipital","lh_parstriangularis",
                                     "lh_lateralorbitofrontal","rh_posteriorcingulate",
                                     "rh_postcentral")],data.clinic)

unci.m.noddi<-lm(Unci_L~sex+age+educ+coc.age.onset+week.dose+years.begin+
              tobc.totyears+ccqn.score+ccqg.score+BIS_cog+BIS_mot+BIS_nonp+
              BIS_tot_score+ASIP_alcohol_use+ASIP_drugs_use+ASIP_psychiatric,data=frame.noddi)
step <- stepAIC(unci.m.noddi, direction = "both", trace = F)
step$call

sfl.m.noddi<-lm(SFL_L~sex+age+educ+coc.age.onset+week.dose+years.begin+
              tobc.totyears+ccqn.score+ccqg.score+BIS_cog+BIS_mot+BIS_nonp+
              BIS_tot_score+ASIP_alcohol_use+ASIP_drugs_use+ASIP_psychiatric,data=frame.noddi)
step <- stepAIC(sfl.m.noddi, direction = "both", trace = F)
step$call

lof.m.noddi<-lm(lh_lateralorbitofrontal~sex+age+educ+coc.age.onset+week.dose+years.begin+
              tobc.totyears+ccqg.score+BIS_cog+BIS_mot+BIS_nonp+
              BIS_tot_score+ASIP_alcohol_use+ASIP_drugs_use+ASIP_psychiatric,data=frame.noddi)
step <- stepAIC(lof.m.noddi, direction = "both", trace = F)
step$call

oper.m.noddi<-lm(lh_parsopercularis~sex+age+educ+coc.age.onset+week.dose+years.begin+
              tobc.totyears+ccqn.score+ccqg.score+BIS_cog+BIS_mot+BIS_nonp+
              BIS_tot_score+ASIP_alcohol_use+ASIP_drugs_use+ASIP_psychiatric,data=frame.noddi)
step <- stepAIC(oper.m.noddi, direction = "both", trace = F)
step$call

rmf.m.noddi<-lm(rh_rostralmiddlefrontal~sex+age+educ+coc.age.onset+week.dose+years.begin+
              tobc.totyears+ccqn.score+ccqg.score+BIS_cog+BIS_mot+BIS_nonp+
              BIS_tot_score+ASIP_alcohol_use+ASIP_drugs_use+ASIP_psychiatric,data=frame.noddi)
step <- stepAIC(rmf.m.noddi, direction = "both", trace = F)
step$call

loc.m.noddi<-lm(rh_lateraloccipital~sex+age+educ+coc.age.onset+week.dose+years.begin+
              tobc.totyears+ccqn.score+ccqg.score+BIS_cog+BIS_mot+BIS_nonp+
              BIS_tot_score+ASIP_alcohol_use+ASIP_drugs_use+ASIP_psychiatric,data=frame.noddi)
step <- stepAIC(loc.m.noddi, direction = "both", trace = F)
step$call

trian.m.noddi<-lm(lh_parstriangularis~sex+age+educ+coc.age.onset+week.dose+years.begin+
              tobc.totyears+ccqn.score+ccqg.score+BIS_cog+BIS_mot+BIS_nonp+
              BIS_tot_score+ASIP_alcohol_use+ASIP_drugs_use+ASIP_psychiatric,data=frame.noddi)
step <- stepAIC(trian.m.noddi, direction = "both", trace = F)
step$call

pcg.m.noddi<-lm(rh_posteriorcingulate~sex+age+educ+coc.age.onset+week.dose+years.begin+
              tobc.totyears+ccqn.score+ccqg.score+BIS_cog+BIS_mot+BIS_nonp+
              BIS_tot_score+ASIP_alcohol_use+ASIP_drugs_use+ASIP_psychiatric,data=frame.noddi)
step <- stepAIC(pcg.m.noddi, direction = "both", trace = F)
step$call

poc.m.noddi<-lm(rh_postcentral~sex+age+educ+coc.age.onset+week.dose+years.begin+
              tobc.totyears+ccqn.score+ccqg.score+BIS_cog+BIS_mot+BIS_nonp+
              BIS_tot_score+ASIP_alcohol_use+ASIP_drugs_use+ASIP_psychiatric,data=frame.noddi)
step <- stepAIC(poc.m.noddi, direction = "both", trace = F)
step$call
```


